Twists of supersymmetric gauge theories

### 2020-01-09 paper.tex
continuing 4d N=2 slowly

\vspace{-10pt}
\paragraph{Fields:}  We can describe the BRST fields of $\mc N=2$ super Yang-Mills with matter valued in the symplectic representation $U$ by restricting the 5d $\mc N=2$ fields from Section \ref{5d_1_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
 \item $U$-valued bosons: a $W$-valued scalar field $\phi \in \Omega^0(\RR^4; W \otimes U)$.
 \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
\begin{prop} \label{4d_2_susy_action_prop}
After reduction to $\mr O(4)$, the 6d $\mc N=(1,0)$ interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_1^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q, \lambda_+^*)(u_+^*,  w_+) + \rho(\d_A \phi_2(w_+ \wedge u_-^*))Q, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q) &= \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \\
I^{(2)}_{\mr{matter}}(Q,Q) &= 
\end{align*}
if $Q=Q^+ \otimes w^+$ is an element of $S_+ \otimes W$, and
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \\
I^{(1)}_{\mr{matter}}(Q) &= \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \\
I^{(2)}_{\mr{matter}}(Q,Q) &= 
\end{align*}
if $Q=Q^- \otimes W_-$ is an element of $S_- \otimes W^*$.
\end{prop}

>>>>

\vspace{-10pt}
\paragraph{Fields:}  We can describe the BRST fields of $\mc N=2$ super Yang-Mills with matter valued in the symplectic representation $U$ by restricting the 5d $\mc N=2$ fields from Section \ref{5d_1_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
 \item $U$-valued bosons: a $W \oplus W^*$-valued scalar field $(\phi \otimes v,\phi' \otimes v') \in \Omega^0(\RR^4; (W \oplus W^*) \otimes U)$.
 \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
It will be enough for our purposes to describe only the action of a chiral supercharge.
\begin{prop} \label{4d_2_susy_action_prop}
After reduction to $\mr O(4)$, the 6d $\mc N=(1,0)$ interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_1^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi')Q_+, \psi_+^*)(v',w_+)) \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
I^{(2)}_{\mr{matter}}(Q,Q) &= 0 %\frac 14 \dvol (Q_+,Q_+)(\psi_+,\psi_+)(w_+ \wedge w_+)
\end{align*}
if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
\end{prop}
